---
title: "Get_CarbonStats_vig"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get_CarbonStats_vig}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(carbonVisR)
```

# Introduction

The `Get_CarbonStats` function is designed to query the Carbon Intensity API for each day within a specified date range and retrieve maximum, average, and minimum intensity values. Additionally, the function provides a convenient way to visualize the intensity trends over time using ggplot.

# Installation

To use the `Get_CarbonStats` function, you need to install the required packages. You can do this by running the following commands:

```{r}
install.packages("httr")
install.packages("dplyr")
install.packages("ggplot2")
```

# Usage

The function takes two parameters: from (start date) and to (end date), both in "YYYY-MM-DD" format. Here is an example of how to use the function:


# Example

Let's use the function to query the Carbon Intensity API for the date range "2023-01-20" to "2023-01-30":

```{r}
# Query the Carbon Intensity API
result <- Get_CarbonStats("2023-01-20", "2023-01-30")

# Access the resulting data frame
data <- result$data

# Access the ggplot object for visualization
plot <- result$plot

# Print the data frame
print(data)

# Plot the ggplot object
print(plot)
```

Feel free to explore additional functionality and customize the visualization to suit your specific needs.
